VM-Centric Snapshot Deduplication\\ for Cloud Data Backup

### 2015-05-22 snapshot_system/mass.tex
change for msst
add copyright info

%\documentclass[10pt,reprint]{socc14}

@@

\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{1}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tang\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
%Wei Zhang$^{\star\dagger}$, Hong Tang$^\dagger$, Hao Jiang$^\dagger$, Tao Yang$^\star$,
%Xiaogang Li$^\dagger$, and Rachael Zeng$^\dagger$ \\
%   {\normalsize $^\star$UC Santa Barbara}\\
%   {\normalsize$^\dagger$Alibaba.com}

}
\maketitle

@@

\input{mass_dedupanalysis}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{ieeetr}
\bibliographystyle{abbrv}
\bibliography{library,dedup1}

>>>>

@@

\author{
\IEEEauthorblockN{Wei Zhang\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}, Daniel Agun\IEEEauthorrefmark{1}, 
Tao Yang\IEEEauthorrefmark{1}, Rich Wolski\IEEEauthorrefmark{1}, 
Hong Tang\IEEEauthorrefmark{3}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of California at Santa Barbara}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Pure Storage Inc.}
\IEEEauthorblockA{\IEEEauthorrefmark{3}Alibaba Inc.}
\IEEEauthorblockA{Email: wei@purestorage.com, \{dagun, tyang, rich\}@cs.ucsb.edu, hongtang@alibaba-inc.com}
}

\IEEEoverridecommandlockouts
\IEEEpubid{978-1-4673-7619-8/15/\$31.00~\copyright~2015 IEEE}
\maketitle

@@

\input{mass_dedupanalysis}
%\bibliographystyle{abbrvnat}
%\bibliographystyle{ieeetr}
\bibliographystyle{abbrv}
\bibliography{library,dedup1,dedup15}

### 2015-05-22 snapshot_system/mass_intro.tex
add copyright info

Our work  considers a backup service with source-side deduplication for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  
This paper extends our preliminary simulation study~\cite{WeiZhangIEEE} to 
restrict the scope of cross-VM deduplication and simplify the deduplication process
by separating popular data chunks and presents the design and implementation of 
a VM-centric backup scheme.  
We term this approach {\em VM-centric} because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
across virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
One consequence of aggressive deduplication is the possible loss of failure
resilience.  If a shared block is lost, all files that
share that block are affected~\cite{Reliability06} and  our work is motivated by this
to develop VM-centric fault isolation techniques.
\comments{
Since the underlying storage file system block size is typically bigger than the average data chunk size
used for deduplication,  packaging
content from different VMs into the same file block  creates a ``false'' sharing that 
affects fault isolation;
}

>>>>

\IEEEpubidadjcol
Our work  considers a backup service with source-side deduplication for converged cloud architectures
that is co-located with user VMs, sharing the cloud compute, network, and
storage resource with them.  
This paper extends our preliminary simulation study~\cite{WeiZhangIEEE} to 
restrict the scope of cross-VM deduplication and simplify the deduplication process
by separating popular data chunks and presents the design and implementation of 
a VM-centric backup scheme.  
We term this approach {\em VM-centric} because the deduplication
algorithm considers VM boundaries in making its decisions as opposed to
treating all blocks as being equivalent within the storage system.
Our work focuses on a tradeoff that allows the sharing of only ``popular'' data blocks 
across virtual machines while using localized deduplication within each VM
to achieve both storage savings and fault isolation.
Another issue addressed is fault  isolation in a content sharing environment caused by deduplication.
One consequence of aggressive deduplication is the possible loss of failure
resilience.  If a shared block is lost, all files that
share that block are affected~\cite{Reliability06} and  our work is motivated by this
to develop VM-centric fault isolation techniques.
\comments{
Since the underlying storage file system block size is typically bigger than the average data chunk size
used for deduplication,  packaging
content from different VMs into the same file block  creates a ``false'' sharing that 
affects fault isolation;
}
